Can the symmetric \textit{Fermi} and eROSITA bubbles be produced by tilted jets: a proof-of-concept study

### 2022-03-30 paper.tex
update

  Second, we observe that\
  the simulated eROSITA bubbles are not as limb-brightened as the observation.\
  A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
  in which CRs could increase the compressibility of the fluid,\
  resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density squared. Also, the disagreement for the northern bubble is expected as the North Polar Spur is generally thought to be caused by a remnant of a local supernova \citep{Egger1995}, which is not included in our simulations.

>>>>

  Second, we observe that\
  the simulated eROSITA bubbles are not as limb-brightened as the observation.\
  A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
  in which CRs could increase the compressibility of the fluid,\
  resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density squared. Also, the disagreement of the northeastern bubble is expected as the North Polar Spur, which is a giant ridge of bright X-ray emission that rises roughly perpendicularly out of the plane of the galaxy, might be a superposition of the GC structure and a remnant of the local supernova \citep{berkhuijsen1971galactic,Das2020,Panopoulou2021}, which is not included in our simulations, whereas analyses based on X-ray data tend to suggest a GC origin \citep{kataoka2018x,sofue2000bipolar,larocca2020analysis}.
